### 2022-11-15 NSF2022/Description/backgroundv3.tex
SA3 done

To determine how the granules move through space, we look for rigid body
transformations
\begin{align}
\label{eq:RBT}
  \FF_i(\XX,t) = R_i(t)(\XX - \aa_i(0)) + \aa_i(t),\quad \XX \in U_i(0),
\end{align}
where $i = 1,\ldots,N_b,$ $R_i(t)$ is an $n
\times n$ rotation matrix, $\aa_i(t)$ are the granule centers, and $\XX$ is a
reference coordinate.
The dynamics come from the following system of semi-linear, elliptic boundary value problems:
\begin{alignat}{4}
  \label{eqn:stokes} 
  -\mu\Delta \uu + \nabla p &= \mathbf{0}, 
  \quad \nabla \cdot \uu = 0, &&\xx \in \Omega(t), \\
  \label{eqn:phase}
  -\epsilon^2 \Delta \phi + W'(\phi) &= 0, &&\xx \in \Omega(t),\\
  \label{eqn:noslip}        
  \frac{d\FF_i}{dt}(\XX,t) & = \uu(\xx) = 
    \vv_i + \oomega_i \times (\xx - \aa_i), 
  \quad &&\xx \in \Gamma_i(t),\\
  \label{eqn:material}
  \phi(\xx) &= h_i(\XX),  &&\xx \in \Gamma_i(t),
\end{alignat}
for $i=1,\ldots,N_b$ and where $\xx = \FF_i(\XX,t)$. Finally,
\begin{align}
\label{eqn:stressbalance}
\int_{\Gamma_i} \left(\sigma  + T_i\right)\nnu \,\dif s = \mathbf{0},\quad
\int_{\Gamma_i} (\xx - \aa_i)\times \left(\sigma + T_i\right) \nnu
  \,\dif s = \mathbf{0},
\end{align}
where
\begin{align}
\label{eqn:hydro_stress}
\sigma = \mu(\nabla \uu + \nabla \uu^T) - pI,\quad 
T_i = \gamma\left(\frac{1}{\epsilon}W(\phi)I + \frac{\epsilon}{2}|\nabla
  \phi|^2 - \epsilon \nabla \phi \nabla \phi^T\right),
%T_i = \gamma\left[\epsilon^{-1} W(\phi)I
%  + \epsilon\left(\tfrac{1}{2}|\nabla \phi|^2I - \nabla \phi \nabla
%  \phi^T\right)\right]
\end{align}
are the hydrodynamic and phase field stresses, respectively.
Equations~\eqref{eqn:stokes} are the Stokes equations describing the
velocity $\uu$ and pressure $p$ of the incompressible fluid region with
viscosity $\mu$. Equation~\eqref{eqn:phase} describes the transitions
of the scalar order parameter $\phi$ with a decay length $\epsilon$.
The scalar function $W(\phi) : \RR \to \RR$ is a nonnegative
well-potential with local minima $\phi_0, \phi_1$, etc., representing
metastable states of the solvent. In the single-well case, $W(\phi) =
\frac{1}{2}\phi^2$ has the minimum $\phi_0 = 0$ and the phase field
equation~\eqref{eqn:phase} becomes the \emph{linear} screened Laplace
equation. In the double-well case e.g, $W(\phi) =
\frac{1}{4}(\phi^2-1)^2+cx$, $c > 0$, the phase field
equation~\eqref{eqn:phase} takes the form of an Allen-Cahn equation with
local minima $\phi_0 < 0 < \phi_1$. Section \ref{sec:specificaim1}
discusses certain modifications needed for~\eqref{eqn:phase} in the
nonlinear case.

\begin{wrapfigure}[21]{r}{3.2in}
  \vspace{-15pt}
  \begin{center}
    \begin{tabular}{m{0.9in}m{0.9in}m{0.9in}}                 
    \includegraphics[width=0.85in]{figures/SpecificAim1/N100B1.jpg}
    &\includegraphics[width=0.85in]{figures/SpecificAim1/N100B2.jpg}
     &\includegraphics[width=0.85in]{figures/SpecificAim1/N100B3.jpg}    \\
    \includegraphics[width=0.85in]{figures/SpecificAim1/N100C1.jpg}
    &\includegraphics[width=0.85in]{figures/SpecificAim1/N100C2.jpg}
      &\includegraphics[width=0.85in]{figures/SpecificAim1/N100C3.jpg}    \\
      \includegraphics[width=0.85in]{figures/SpecificAim1/N100A1.jpg}
      &\includegraphics[width=0.85in]{figures/SpecificAim1/N100A2.jpg}
      &\includegraphics[width=0.85in]{figures/SpecificAim1/N100A3.jpg} 
  \end{tabular}
  \end{center}
  \vspace{-20pt}
  \caption{\footnotesize \label{fig:self-assembly2} Changes in the
  boundary condition \eqref{eqn:material} yield distinct morphologies.
  Each row has the same initial configuration; $W(\phi) =
  \tfrac{1}{2}\phi^2$. (\emph{Top}) Granules with an amphiphilic
  boundary condition form bilayer configurations (yellow, $\phi = 1$,
  blue, $\phi = 0$). (\emph{Middle}) Granules with $\phi = 2$ (magenta)
  on one side and $\phi = 1$ (yellow) on the other form multilamellar
  bilayers.  (\emph{Bottom}) Bipolar granules with $\phi = 1$ (yellow)
  on one side and $\phi=-1$ (green) on the other side form a
  checkerboard pattern.}
\end{wrapfigure}

@@

\subsection{Outline of the proposal}
The aim of this proposal is to advance the theory, simulation and
modeling for soft-matter systems and foster training in Mathematical
Sciences.  Section~\ref{sec:BroaderImpacts} summarizes the broader
impacts and section~\ref{sec:IntellectualMerit} summarizes the
intellectual merit of our research activity.
Section~\ref{sec:proposed-work} contains our specific aims.

>>>>

To determine how the granules move through space, we look for rigid body
transformations
\begin{align}
\label{eq:RBT}
  \FF_i(\XX,t) = R_i(t)(\XX - \aa_i(0)) + \aa_i(t),\quad \XX \in U_i(0),
\end{align}
where $i = 1,\ldots,N_b,$ $R_i(t)$ is an $n
\times n$ rotation matrix, $\aa_i(t)$ are the granule centers, and $\XX$ is a
reference coordinate.
The dynamics come from the following system of semi-linear, elliptic boundary value problems:
\begin{alignat}{4}
  \label{eqn:stokes} 
  -\mu\Delta \uu + \nabla p &= \mathbf{0}, 
  \quad \nabla \cdot \uu = 0, &&\xx \in \Omega(t), \\
  \label{eqn:phase}
  -\epsilon^2 \Delta \phi + W'(\phi) &= 0, &&\xx \in \Omega(t),\\
  \label{eqn:noslip}        
  \frac{d\FF_i}{dt}(\XX,t) & = \uu(\xx) = 
    \vv_i + \oomega_i \times (\xx - \aa_i), 
  \quad &&\xx \in \Gamma_i(t),\\
  \label{eqn:material}
  \phi(\xx) &= h_i(\XX),  &&\xx \in \Gamma_i(t),
\end{alignat}
for $i=1,\ldots,N_b$ and where $\xx = \FF_i(\XX,t)$. Finally,
\begin{align}
\label{eqn:stressbalance}
\int_{\Gamma_i} \left(\sigma  + T_i\right)\nnu \,\dif s = \mathbf{0},\quad
\int_{\Gamma_i} (\xx - \aa_i)\times \left(\sigma + T_i\right) \nnu
  \,\dif s = \mathbf{0},
\end{align}
where
\begin{align}
\label{eqn:hydro_stress}
\sigma = -pI + \mu(\nabla \uu + \nabla \uu^T),\quad 
T_i = \gamma\left(\frac{1}{\epsilon}W(\phi)I + \frac{\epsilon}{2}|\nabla \phi|^2I - \epsilon \nabla \phi \nabla \phi^T\right)
%T_i = \gamma\left[\epsilon^{-1} W(\phi)I
%  + \epsilon\left(\tfrac{1}{2}|\nabla \phi|^2I - \nabla \phi \nabla
%  \phi^T\right)\right]
\end{align}
are the hydrodynamic and phase field stresses, respectively.
Equations~\eqref{eqn:stokes} are the Stokes equations describing the
velocity $\uu$ and pressure $p$ of the incompressible fluid region with
viscosity $\mu$. Equation~\eqref{eqn:phase} describes the transitions
of the scalar order parameter $\phi$ with a decay length $\epsilon$.
The scalar function $W(\phi) : \RR \to \RR$ is a nonnegative
well-potential with local minima $\phi_0, \phi_1$, etc., representing
metastable states of the solvent. In the single-well case, $W(\phi) =
\frac{1}{2}\phi^2$ has the minimum $\phi_0 = 0$ and the phase field
equation~\eqref{eqn:phase} becomes the \emph{linear} screened Laplace
equation. In the double-well case e.g, $W(\phi) =
\frac{1}{4}(\phi^2-1)^2+cx$, $c > 0$, the phase field
equation~\eqref{eqn:phase} takes the form of an Allen-Cahn equation with
local minima $\phi_0 < 0 < \phi_1$. Section \ref{sec:specificaim1}
discusses certain modifications needed for~\eqref{eqn:phase} in the
nonlinear case.

\begin{wrapfigure}[21]{r}{3.2in}
  \vspace{-15pt}
  \begin{center}
    \begin{tabular}{m{0.9in}m{0.9in}m{0.9in}}                 
    \includegraphics[width=0.85in]{figures/SpecificAim1/N100B1.jpg}
    &\includegraphics[width=0.85in]{figures/SpecificAim1/N100B2.jpg}
     &\includegraphics[width=0.85in]{figures/SpecificAim1/N100B3.jpg}    \\
    \includegraphics[width=0.85in]{figures/SpecificAim1/N100C1.jpg}
    &\includegraphics[width=0.85in]{figures/SpecificAim1/N100C2.jpg}
      &\includegraphics[width=0.85in]{figures/SpecificAim1/N100C3.jpg}    \\
      \includegraphics[width=0.85in]{figures/SpecificAim1/N100A1.jpg}
      &\includegraphics[width=0.85in]{figures/SpecificAim1/N100A2.jpg}
      &\includegraphics[width=0.85in]{figures/SpecificAim1/N100A3.jpg} 
  \end{tabular}
  \end{center}
  \vspace{-20pt}
  \caption{\footnotesize \label{fig:self-assembly2} Changes in the
  boundary condition \eqref{eqn:material} yield distinct morphologies.
  Each row has the same initial configuration; $W(\phi) =
  \tfrac{1}{2}\phi^2$. (\emph{Top}) Granules with an amphiphilic
  boundary condition form bilayer configurations (yellow, $\phi = 1$,
  blue, $\phi = 0$). (\emph{Middle}) Granules with $\phi = 2$ (magenta)
  on one side and $\phi = 2$ on the other form multilamellar bilayers.
  (\emph{Bottom}) Bipolar granules with $\phi = 1$ (yellow) on one side
  and $\phi=-1$ (green) on the other side form a checkerboard pattern.}
\end{wrapfigure}

@@

\subsection{Outline of the proposal}
The aim of this proposal is to advance the theory, simulation and
modeling for soft-matter systems and foster training in Mathematical
Sciences.
The success of the proposed research requires complementary expertise
and collaborative efforts in physics, applied mathematics, and
scientific computing. The PIs' recent collaborative
works~\cite{FuQuRyYo22, fu-ryh-qua-you2022,FuQuRyYo22}
are a solid foundation for the proposed research.

Section~\ref{sec:BroaderImpacts} summarizes the broader
impacts and section~\ref{sec:IntellectualMerit} summarizes the
intellectual merit of our research activity.
Section~\ref{sec:proposed-work} contains our specific aims.
